Data Appendix to \"The impact of weather events on schooling outcomes\

### 2020-03-19 data_appendix.Rmd
Commit merging changes

```{r setup, echo = F, message = F}
knitr::opts_chunk$set(results = 'asis', cache = F)
library(tidyverse)
library(summarytools)
st_options(plain.ascii = F,
           style = "rmarkdown",
           footnote = NA,
           subtitle.emphasis = F,
           dfSummary.silent = T,
           dfSummary.valid.col = F,
           tmp.img.dir = "./tmp",
           dfSummary.style = "grid")
# add haven package to make stata 16 version readable 
library(foreign)
library(haven)

@@

- **hh_id:** This variable is the household ID, which is the same for each member of the household. It is made up of letters and numbers. 
- **nro1:** Description of second variable.
- **members:** 
- **urb_rur:** 
- **urb_rur:** 
- **urb_rur:**

@@

```{r import household data}
data_2005 <- read_dta(file.path("Raw data","seminar_paper_data","2005_hhsurvey.dta")) %>% 
  rename(hh_id = folio,
        assist = s3_08,  
        reason = s3_09, 
        members = nm_y,
        sex = s1_02,
        age = s1_03,
        relation = s1_05,
        literacy = s3_01,
        register = s3_04,
        grade = s3_05b,
        repeated = s3_07)
# it looks like you need to add dept = xxx to the list above since dept is not showing up as a variable for me        
hh_2005 <- data_2005 %>% 
  select(hh_id, assist, reason, members, sex, age, relation, literacy, register, grade, repeated, dept)
```

@@

## Weather data
**Citation:** Put citation here in APA or other consistent format that you will use throughout the project. Include a hyperlink if applicable.  
**DOI:** If the dataset has a documention identified (DOI) assigned put it here.  
**Date Downloaded:** Identify when you downloaded the dataset.  
**Filename(s):** raw_data/filename.csv *If you have a large number of files you can use a patten (see visit data below)*
**Unit of observation:** What distinguishes different rows in your dataset?  
**Dates covered:** What time frame does the data cover?

@@

```{r import weather data}
weather <- read_csv(file.path("Raw data", "recurrencia_inundacion2002_2012bol.csv")) %>% 
  rename(dept = NOM_DEP, flood = A_2005)

@@

`export_summary_table(dfSummary(dataset_name))`
```

>>>>

```{r setup, echo = F, message = F}
knitr::opts_chunk$set(results = 'asis', cache = F)
library(tidyverse)
library(summarytools)
st_options(plain.ascii = F,
           style = "rmarkdown",
           footnote = NA,
           subtitle.emphasis = F,
           dfSummary.silent = T,
           dfSummary.valid.col = F, 
           tmp.img.dir = "./tmp",
           dfSummary.style = "grid")

# add haven package to make stata 16 version readable 
library(foreign)
library(haven)

@@

- **hh_id:** This variable is the household ID, which is the same for each member of the household. It is made up of letters and numbers. 
- **nro1:** Description of second variable.
- **assist:** 
- **urb_rur:** 
- **reason:** 
- **members:** 
- **sex:** 
- **age:** 
- **relation:** 
- **literacy:** 
- **register:**
- **grade:** 
- **repeated:** 
- **dept:**

@@

```{r import household data}
data_2005 <- read_dta(file.path("Raw data","seminar_paper_data","2005_hhsurvey.dta")) %>% 
  rename(hh_id = folio,
        assist = s3_08,  
        reason = s3_09, 
        members = nm_y,
        sex = s1_02,
        age = s1_03,
        relation = s1_05,
        literacy = s3_01,
        register = s3_04,
        grade = s3_05b,
        repeated = s3_07,
        dept = depto)
hh_2005 <- data_2005 %>% 
  select(hh_id, assist, reason, members, sex, age, relation, literacy, register, grade, repeated, dept)
```

@@

## Flood data
**Citation:** Put citation here in APA or other consistent format that you will use throughout the project. Include a hyperlink if applicable.  
**DOI:** If the dataset has a documention identified (DOI) assigned put it here.  
**Date Downloaded:** Identify when you downloaded the dataset.  
**Filename(s):** raw_data/filename.csv *If you have a large number of files you can use a patten (see visit data below)*
**Unit of observation:** What distinguishes different rows in your dataset?  
**Dates covered:** What time frame does the data cover?

@@

## Flood data
**Citation:** Put citation here in APA or other consistent format that you will use throughout the project. Include a hyperlink if applicable.  
**DOI:** If the dataset has a documention identified (DOI) assigned put it here.  
**Date Downloaded:** Identify when you downloaded the dataset.  
**Filename(s):** raw_data/filename.csv *If you have a large number of files you can use a patten (see visit data below)*
**Unit of observation:** What distinguishes different rows in your dataset?  
**Dates covered:** What time frame does the data cover?

### Data import code and summary
```{r import flood data}
flood <- read_csv(file.path("Raw data", "recurrencia_inundacion2002_2012bol.csv")) %>% 
  rename(dept = NOM_DEP, flood = A_2005)

@@

`export_summary_table(dfSummary(flood_summary))`
```

## Drough data
**Citation:** Put citation here in APA or other consistent format that you will use throughout the project. Include a hyperlink if applicable.  
**DOI:** If the dataset has a documention identified (DOI) assigned put it here.  
**Date Downloaded:** Identify when you downloaded the dataset.  
**Filename(s):** raw_data/filename.csv *If you have a large number of files you can use a patten (see visit data below)*
**Unit of observation:** What distinguishes different rows in your dataset?  
**Dates covered:** What time frame does the data cover?

```{r importing droughts data, echo = F, message = F}
#drought data set 
drought <- read_csv("Raw data\\recurrenciasequia_2002_2012bol.csv")
# modify this section following the template with the flood data, but wait until we've gotten the pivot_longer() function working so you don't duplicate effort.
#rename variables
drought <- rename(weather, c(NOM_DEP = "dept"))
drought <- rename(weather, c(A_2005 = "drought"))

library(dplyr)
drought %>% 
  group_by(dept) %>% 
  summarise(drought = sum(drought))
